VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper.tex
r

\begin{document}

%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
\title{
VM-Centric  Snapshot Deduplication  with Fault Isolation 
for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  {\normalsize$^\star$  University of California at Santa Barbara}, {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

@@

\begin{small}
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{small}
\end{document}

>>>>

\linespread{.98} % to squeeeze lines and put figures in same page
\begin{document}

%\title{VM-Centric Deduplication with Fault Isolation for Virtual Machine Snapshot Backup }
%Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud}
\title{
VM-Centric  Snapshot Deduplication  with Fault Isolation 
for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\author{
  Wei Zhang$^{\star}$, Michael Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  {\normalsize$^\star$  University of California at Santa Barbara} {\normalsize$^\dagger$Alibaba Inc.} \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}

@@

\begin{small}
\linespread{.90} % to squeeeze lines and put figures in same page
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{small}
\end{document}

### 2014-01-31 snapshot_system/paper_eval.tex
r

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.
\subsection{Settings}
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

\subsection{Fault Isolation and Snapshot Availability}

@@

\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,%use ! before a row in the data table to exclude it
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO ($r=3$) and VC ($r_c=6$, $r=3$).}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htb]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
  \label{fig:pds-replication}
\end{figure}

\subsection{Competitiveness of Deduplication Efficiency}
\label{sect:evaldedup}

@@

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
     no-simi&   &&  &    \\ \hline
     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

>>>>

We will compare VC with a VO approach  using stateless routing with binning (SRB) 
based on~\cite{Dong2011,extreme_binning09}.
SRB executes distributed deduplication by routing data chunks to cluster machines~\cite{Dong2011}
using  a min-hash function discussed in \cite{extreme_binning09}. Once a data chunk is routed to
a machine, the chunk is compared with the fingerprint index within this machine locally based 
on~\cite{extreme_binning09}.

{\bf Settings}.
We have performed a trace-driven study based on a production dataset~\cite{WeiZhangIEEE} from 
Alibaba Aliyun's cloud platform with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

%\subsection{Fault Isolation and Snapshot Availability}
\subsection{Snapshot Availability}

@@

\begin{table}[htbp]
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,%use ! before a row in the data table to exclude it
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO ($r=3$) and VC ($r_c=6$, $r=3$).}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees on a $p=100$-node cluster.}
  \label{fig:pds-replication}
\end{figure}

\subsection{Deduplication Efficiency}
\label{sect:evaldedup}

@@

\comments{
alg     efficiency
\scriptsize{}VC-2\%\tiny{}No\ Similarity        94.3132243792193
\scriptsize{}VC-NoPDS   93.0202119345744
\scriptsize{}VC-2\%PDS  96.0127647380588
\scriptsize{}VC-4\%PDS  96.5784837160482
\scriptsize{}SRB        97.8625610883421
}
\begin{table}[htbp]
\begin{small}
    \begin{tabular}{|c|c|c|c|c|}
    \hline
     \multicolumn{4}{|c|}{VC}  & VO \\ \hline
     2\%PDS  &  No PDS &2\%PDS     & 4\%PDS & SRB  \\ 
     no-simi&   &&  &    \\ \hline
     94.31\%& 93.02\%  & 96.01\% & 96.58\% & 97.86\% \\ \hline
    \end{tabular}
\end{small}
    \caption{Deduplication efficiency for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}
